\textbf{Causal graph quantum dynamic simulation}

### 2021-06-07 v5/paper/paper.tex
adding debuging print to find the memory error

\begin{lstlisting}[style=CStyle]
class graph {
	// variables 
	graph_name_t* name_;
	std::vector<unsigned int> left_;
	std::vector<unsigned int> right_;

@@

The fonction to step all particules uses the fonctions "rotate\_once\_left" and "rotate\_once\_right" which rotate particules if they overflow:

@@

  		rotate_once_right(right_);
  		rotate_once_left(left_);
  	}
  	//...
\end{lstlisting}

@@

  		rotate_once_right(left_);
  		rotate_once_left(right_);
  	}
  	//...
\end{lstlisting}

@@

		// check for last merge
		if (split_merge.back() == split_merge_t(size() - 1, merge_t)) {
			name_->merge(size() - 1);
			overflow_right(left_);	
			split_merge.pop_back();
		}

		// check for first element split 
		bool first_split = false;

		// and calculating max displacement 
		int total_displacement = 0;
		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
			if (type == split_t) {
				++total_displacement;
			} else
				--total_displacement;

		// reserve space for nodes
		name_->reserve(total_displacement);

		// split and merge names
		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
			if (type == split_t) {
				first_split |= name_->split(pos);
			} else
				name_->merge(pos);

		// move particules
		auto const split_merge_begin = split_merge.rend();
		int displacement = total_displacement;
		auto split_merge_it = split_merge.rbegin();
		for (auto &left_it : left_ | std::ranges::views::reverse) {
			// check if there are any nodes left
			for (;split_merge_it->first >= left_it && split_merge_it != split_merge_begin; ++split_merge_it)
				// check if the node is split or merged
				if (split_merge_it->second == split_t) {
						--displacement; // decrement the displacement 
					} else
						++displacement; // decrement the displacement

			//check if we can exit
			if (split_merge_it == split_merge_begin && displacement == 0)
				break;

			left_it += displacement;
		}

		/* we than do the exact same thing with particule going to the right, rplacing ">=" at line 42 by a ">" */

		// finish first split 
		if (first_split) {
			rotate_once_left(left_);
			rotate_once_left(right_);
		}
	}
	//...
\end{lstlisting}

@@

@@

		// left hash 
		for (auto &l : left_)
			boost::hash_combine(hash_, l);

@@

	  	// right hash 
	  	for (auto &r : right_)
	   		boost::hash_combine(hash_, r);

@@

	  	// name hash 
	  	boost::hash_combine(hash_, name_->hash());

@@

To get the list of all indeces of splits and merges, we iterate through both the "left" and "right" positions, iterating the one that is the smallest so that it always converges towars positions that match (or are one apart for merges):

\begin{lstlisting}[style=CStyle]
/* function to get all split and merges */
std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
	std::vector<graph::op_t> split_merge;

	unsigned int const last_idx = graph->size() - 1;

	auto left_it = graph->left().begin();
	auto right_it = graph->right().begin();
	bool first_or_last_split = *left_it == *right_it && *left_it == 0;
	first_or_last_split |= graph->left().back() == last_idx && graph->right().back() == last_idx;

	while (right_it < right_end = graph->right().end() && left_it < graph->left().end())
		if (*left_it == *right_it) {
			// check for split
			split_merge.push_back({*left_it, graph->split_t});

			++right_it;
			++left_it;
		} else if (*left_it < *right_it) {
			// chedk for merges
			if (*left_it == *right_it - 1)
				if (left_it == graph->left().end() - 1) {
					split_merge.push_back({*left_it, graph->merge_t});
				} else if (*(left_it + 1) != *right_it)
					split_merge.push_back({*left_it, graph->merge_t});

			++left_it;
		} else
			++right_it;

	if (!first_or_last_split)
		if (graph->left().back() == last_idx && graph->right()[0] == 0)
			split_merge.push_back({last_idx, graph->merge_t});

	return split_merge;
}
\end{lstlisting}

@@

\begin{lstlisting}[style=CStyle]
	//...
	void reduce_all() {
		for(auto it = graphs_.begin(); it != graphs_.end();) {
			// range of similar graphs to delete
			auto upper = graphs_.equal_range(it->first).second;

			for(auto jt = std::next(it); jt != upper; ++jt)
		    	it->second += jt->second;

			// if the first graphgs has a zero probability, erase the whole range
			if (!check_zero(it->second))
				++it;

			it = graphs_.unsafe_erase(it, upper);
		}
	}
	//...
\end{lstlisting}

@@

		#pragma omp parallel
		#pragma omp single
		for (auto & [graph, mag] : buff)
		#pragma omp task
		{
			auto graphs = rule(graph);
			for (auto & [graph_, mag_] : graphs)
			#pragma task
	  			graphs_.insert({graph_, mag_ * mag});
		}
	}
	//...
}
\end{lstlisting}

>>>>

\begin{lstlisting}[style=CStyle]
class graph {
	// split_merge type enum 
  	typedef enum op_type {
		split_t,
		merge_t,
		erase_t,
		create_t,
	} op_type_t;

	// typedef of the pair of an index and a op_type 
  	typedef std::pair<unsigned int, op_type_t> op_t;

	// variables 
	graph_name_t name_;
	std::vector<char /*bool*/> left;
	std::vector<char /*bool*/> right;

@@

@@

  		std::rotate(left.begin(), left.begin() + 1, left.end());
		std::rotate(right.rbegin(), right.rbegin() + 1, right.rend());
  	}
  	//...
\end{lstlisting}

@@

  		std::rotate(left.rbegin(), left.rbegin() + 1, left.rend());
		std::rotate(right.begin(), right.begin() + 1, right.end());
  	}
  	//...
\end{lstlisting}

@@

		bool first_split = false;
		auto const size_ = size();
		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
			if (type == split_t) {
				first_split |= name_.split(pos);

				// change right
				right[pos] = false;

				//insert
				right.insert(right.begin() + pos + 1, true);
				left.insert(left.begin() + pos + 1, false);
			} else if (type == merge_t) {
				name_.merge(pos);

				// next pos
				unsigned short int next_pos = (pos + 1) % size_;

				// change left
				left[next_pos] = true;

				//erase
				right.erase(right.begin() + pos);
				left.erase(left.begin() + pos);
			}

		/* finish first split */
		if (first_split) {
			std::rotate(left.begin(), left.begin() + 1, left.end());
			std::rotate(right.begin(), right.begin() + 1, right.end());
		}
	}
	//...
\end{lstlisting}

\subsubsection{erase\_create()}

\begin{lstlisting}[style=CStyle]

void inline graph::erase_create(std::vector<op_t>& erase_create) {
	//...
	void inline erase_create(std::vector<op_t>& erase_create) {
		if (erase_create.empty())
			return;

		for (auto & [pos, type] : erase_create)
			if (type == erase_t) {
				left[pos] = false;
				right[pos] = false;
			} else if (type == create_t) {
				left[pos] = true;
				right[pos] = true;
			}
	}
	//...
\end{lstlisting}

@@

		// save memory 
		left.shrink_to_fit();
		right.shrink_to_fit();

@@

		// left hash 
		auto const size_ = size();
		for (short int i = 0; i < size_; ++i)
			if (left[i])
				boost::hash_combine(hash_, i);

@@

	  	// right hash 
	  	for (short int i = 0; i < size_; ++i)
			if (right[i])
				boost::hash_combine(hash_, i);

@@

	  	// name hash 
	  	boost::hash_combine(hash_, name_.hash());

@@

\begin{lstlisting}[style=CStyle]
/* function to get all split and merges */
std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
	std::vector<graph::op_t> split_merges;

	auto const size_ = graph.size();
	for (int i = 0; i < size_; ++i)
		if (graph.left[i] && graph.right[i]) {
			split_merges.push_back({i, graph.split_t});
		} else {
			// next pos
			unsigned short int next_pos = (i + 1) % size_;

			if (graph.left[i] && graph.right[next_pos] && !graph.left[next_pos])
				split_merges.push_back({i, graph.merge_t});
		}

	return split_merges;
}
\end{lstlisting}

\subsubsection{get\_erase\_create()}

\begin{lstlisting}[style=CStyle]
std::vector<graph::op_t> inline get_erase_create(graph_t const &graph) {
	std::vector<graph::op_t> create_erases;

	for (int i = 0; i < graph.size(); ++i)
		if (graph.left[i] && graph.right[i]) {
			create_erases.push_back({i, graph.erase_t});
		} else if (!graph.left[i] && !graph.right[i])
			create_erases.push_back({i, graph.create_t});

	return create_erases;
}
\end{lstlisting}

@@

\begin{lstlisting}[style=CStyle]
	//...
	void reduce_all() {
		graph_map_t buff; // faster, parallel reduce that uses WAY more ram
		buff.swap(graphs_);

		#pragma omp parallel
		#pragma omp single
	    for(auto it = buff.begin(); it != buff.end();) {
	    	// range of similar graphs to delete
	    	auto const graph = it->first;
	    	auto const range = buff.equal_range(graph);

	    	// next iteration
	    	it = range.second;

	    	#pragma omp task
	    	{
	    		std::complex<long double> acc = 0;
	    		for(auto jt = range.first; jt != range.second; ++jt)
	        		acc += jt->second;

		    	// if the first graphgs has a zero probability, erase the whole range
		    	if (!check_zero(acc))
		    		graphs_.insert({graph, acc});
	    	}
	    }
	}
	//...
\end{lstlisting}

@@

		#pragma omp parallel
		#pragma omp single
		for (auto & [graph, mag] : buff)
		#pragma omp task
		{
			auto const graphs = rule(graph);
			for (auto & [graph_, mag_] : graphs)
			#pragma task
	  			graphs_.insert({graph_, mag_ * mag});
		}
	}
	//...
}
\end{lstlisting}
